When are Fuzzy Extractors Possible?

### 2014-10-07 trunk/info-bounds/FuzzyExtPossibility.tex
moved known distribution case

\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
We discuss known distribution algorithms in \secref{sec:known distributions def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = \key] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.  
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:

@@

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.  We now describe the known distribution setting.

\subsection{Known Distribution Algorithms}
\label{sec:known distributions def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

\begin{definition}
Let $F : \mathcal{K} \times \mathcal{M} \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in \mathcal{M}$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
\end{definition}

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t,W,max}|-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |B_{t,W,max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t,W,max}| + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t,W,max}| - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t,i,W, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t,W_i,max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
\]

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t,W_i,max}|-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

@@

\begin{corollary}
\label{cor:extension to fuzz ext}
Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.  (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
\end{corollary}

>>>>

\subsection{Fuzzy Extractors and Secure Sketches}\label{sec:fuzz extractor}

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
%We discuss known distribution algorithms in \secref{sec:known distributions def}.  
Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent
In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known in order for the correctness guarantee to hold: correctness holds for any $w'$ with probability $1-\delta$ over the coins of the algorithms, but $w'$ cannot be a function of the output of  $\sketch(w)$.

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{If we wish to be pedantic and extend correctness to all of $\mathcal{M}$, we can define $\gen$/$\sketch$ to be the identity function on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this will not harm security}.

Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them. Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

\paragraph{From Secure Sketches to Fuzzy Extractors}
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:

@@

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy. % We now describe the known distribution setting.

%\subsection{Known Distribution Algorithms}
%\label{sec:known distributions def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
%We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
%
%\begin{definition}
%Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution %secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
%\begin{enumerate}
%\item \emph{Correctness:} 
%$
%\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
%Correctness is guaranteed only for the support of $W$.
%\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

\begin{definition}[\cite{DBLP:journals/jcss/CarterW79}]
Let $F : \mathcal{K} \times \mathcal{M} \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in \mathcal{M}$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
\end{definition}

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
\[
\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
\]

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

@@

\begin{corollary}
\label{cor:extension to fuzz ext}
Let $\mathcal{M}$ be a metric space where $n = \log |\M|$.
For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.  (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
\end{corollary}
